---
title: "fars_tools"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fars_tools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, 
  echo = FALSE, message = FALSE, 
  eval=F, 	#Run the R code?
  messages=F, #	Print out messages?
  warnings=F, 	#Print out warnings?
  include=F, 	#If FALSE, run code, but don’t print code or results
  warning = FALSE,
  comment = "#>"
)
```

```{r setup}
library(farsUSA)
```

## Practical note
Package `farsUSA` was the practical exercise of the course *Building R-packages* included in the *+Coursera+* *Mastering Software Development in R*
## Introduction 
This package reads *fars* data and is able to summarize and represents accidents data for each year and USA state.

## Functions
This package has internal functions devoted to read and prepare data from source, and two practical functions for summarizing and ploting data.

### Internal functions

#### fars_read
*read a csv text file*

This function reads a csv format file and stores in dataframe tbl_df. For this task uses package "readr" which allows to directly read comressed files

@param filename A character chain containing the name of the file you want to read

@return This function returns a dataframe tbl_df


```{r examples: fars-read}
fars_read("accident_2013.csv.bz2")
```

#### make_filename
*Creates a file name*

This function creates the apropriate name of the the file corresponding to accident data for the year 'year'

@param year An integer indicating the year for filename creation

@return This function returns a character variable containing a file name

```{r examples: make_filename}
make_filename(2013)
```

#### fars_read_years
*Reads several csv text files*

This function reads several csv format files and stores month and year into a list of dataframes tbl_df,
containing month and year of the accidents stored, one tbl_df for each csv file.

@param years A list containing the years to estract information

@return This function returns a list of tbl_df from all years in "years" with month and year information

```{r examples: fars_read_years}
fars_read_years(list(2013,2014))
```



### User functions

#### fars_summarize_years
*Summarizes accidents by year and month*

This function summarizes the number of accidents occurred each month for a list of years

@param years A list of years

@return This function returns a tbl_df containing number of accidents by month
for the years included in the list parsed as parameter

```{r examples: fars_summarize_years}
fars_summarize_years(list(2014,2015))
```

#### fars_map_state
*Print a map of crash over year and state of U.S.*

This function prints a map with the position of every crash occurred over the state 'state.num' and the year 'year'

@param state.num integer with the number of desired state, ranging 1:56
@param year An integert with the desired year

@return This function returns a map


```{r examples: fars_map_state}
fars_map_state(1, 2013)
```

